Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-05 doc/main_jfm.tex
updates

\todo[inline]{Introduce dimensionless shear rate here}

@@

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate 
is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity is used through this work.

@@

\todo[inline]{Figure/Table of the friction coefficient for different
shear rates}

@@

\todo[inline]{Stream lines not right. Need to subtract a constant
velocity instead of the background flow.}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
  }
    \label{figure6}
\end{figure}

@@

\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
JCP paper by Rahimian, Veerapaneni, and Biros.}

>>>>

\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}

@@

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.

@@

\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}

\begin{equation}
b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_\Sigma R \dot\theta dS}.
\end{equation}

\begin{table}[ht] 
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c}
\hline\hline                    
Case $i$ & $\dot\gamma$ & $b_i$\\
\hline 
1 & 0.020 &  5.1648  \\
2 & 0.025 &  5.2027  \\ 
3 & 0.050 &  5.1944   \\ [1ex]
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
  }
    \label{figure6}
\end{figure}

@@

%\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
%JCP paper by Rahimian, Veerapaneni, and Biros.}
